Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-04-04 chapters/ch_data_analysis.tex
General Backup

@@

This is done for all the systems. I NEED TO PUT THE ASSUMPTIONS OF 132 108 HERE!!!

@@

\subsection{MC and Data Comparison}
Add Figure of Pad response function for pion,proton.... for MC vs Data vs angles...
Add Figure of Number of clusters of MC vs Data
Add Figure of dEdx MC vs Data
Add Figure of Momentum resolution MC vs Data
Add Figure of track residuals? MC vs data?

>>>>

MAYBE ADD A LITTLE NAPKIN CALCULATION OF SPACE CHARGE TO SHOW ORDER OF EFFECT.

@@

This is done for all the systems. I NEED TO PUT THE ASSUMPTIONS of SPACE CHARGE SHEET DENSITY OF 132 108 HERE!!!

From the BDC tracking, the precise interaction point on target is known. Using this point greatly improves the momentum resolution of the track fitting, but there is a systematic shift when comparing the momentum value without using the vertex BDC point in the fit. The space charge affects right-going and left-going tracks differently making right-going tracks more rigid (higher momentum) and left-going tracks less rigid (lower momentum). For polar angles of $\theta < 40 \deg$, the disagreement between momentum values fitted with the BDC, versus without, are much less because the projection of the track does not disagree as much with the BDC point as tracks with polar angles of $\theta > 40 \deg$. This is seen in

@@

\subsection{MC and Data Comparison}

\begin{figure}[!hbt]
\includegraphics[width=\linewidth]{numcluster.png}
\caption{Comparison of MC to data.}
\label{fig:clustcomp}
\end{figure}

\begin{figure}[!hbt]
\includegraphics[width=\linewidth]{poca.png}
\caption{Comparison of MC to data.}
\label{fig:pocacomp}
\end{figure}

Add Figure of Pad response function for pion,proton.... for MC vs Data vs angles...
Add Figure of Number of clusters of MC vs Data
Add Figure of dEdx MC vs Data
Add Figure of Momentum resolution MC vs Data
Add Figure of track residuals? MC vs data?

\section{Aligning TPC}

\section{CoBo timing correction}

### 2020-04-04 chapters/ch_data_analysis_2.tex
Adding better tables and gas section. Macros folder added
Pion spectra added
General Backup

\chapter{Data Analysis II: Extracting Physics}
\section{Beam Particle Identification}
\section{Event Mixing}
\section{Reaction Plane Determination}

>>>>

\chapter{Data Analysis II: Extracting Physics}

\section{Edge Cuts}
As seen in Fig.~\ref{fig:edge}, edges of the measurement volume of the TPC we can see several edge effects distortion the clusters positions. The last pads on the edges of the pad-plane naturally have no neighbors on the outsides, therefore their cluster position is biased towards the inside of the TPC. Also since we measure a finite window in time for the vertical direction, pulses near the edge of the time-bucket window are clipped and the reconstructed times are biased towards inside the TPC volume.

The number of clusters affected is small but the deviation at the end of the track is enough to start causing issues in the momentum reconstruction. Simple cuts around the left,right, top, and bottom of the TPC remove these clusters from the analysis,

\begin{equation*}
  |x|\geq420~\mathrm{mm},\quad y\leq-522+\mathrm{y_o}~\mathrm{mm},
  \quad\mathrm{and}\quad y\geq-64+\mathrm{(Hit\ Shift)}~\mathrm{mm}.
  \label{eq:hitshift}
\end{equation*}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{clusterLR.png} 
        \caption{Generic} \label{fig:mom_S_before}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{clusterTop.png} 
        \caption{Competitors} \label{fig:mom_L_before}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{clusterBottom.png} 
        \caption{Generic} \label{fig:mom_S_after}
    \end{subfigure}

\label{fig:edge}
\end{figure}

\section{High Density Cut}
The density of tracks near the target region is very high and most of electronics information from this region is inaccurate in both timing and charge value. Hits lying within an semi-ellipsoidal cut region around the target are removed from the software and not included in the track and momentum reconstruction.

Add picture of ellipsoid

\section{Beam angle selection}
The beam is bent by the magnetic field before hitting the target. The BDCs track the beam outside of the magnet. The beam is then propagated through the magnetic field until the target position. The beam angle on target is categorized by two angles $\theta_{a,proj}$ and $\theta_

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn108.png} 
        \caption{Generic} \label{fig:mom_S_before}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn112.png} 
        \caption{Competitors} \label{fig:mom_L_before}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn124.png} 
        \caption{Generic} \label{fig:mom_S_after}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn132.png} 
        \caption{Competitors} \label{fig:mom_L_after}
    \end{subfigure}
\label{fig:mom_sc}
\end{figure}

\section{Vertex Cut}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{vertex-Sn108.png} 
        \caption{$\tin{108}{124}$ vertex distributon for all runs.} \label{fig:vertex108}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{vertex-Sn112.png} 
        \caption{$\tin{112}{124}$ vertex distributon for all runs.} \label{fig:vertex112}
    \end{subfigure}

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{vertex-Sn124.png} 
        \caption{$\tin{124}{112}$ vertex distributon for all runs.} \label{fig:vertex124}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\linewidth]{vertex-Sn132.png} 
        \caption{$\tin{132}{124}$ vertex distributon for all runs.} \label{fig:vertex132}
    \end{subfigure}
\label{fig:vertexdist}
\end{figure}

\section{Impact Parameter Selection}

\section{Track Quality Cuts}

\section{Angular Quality Cuts}

### 2020-04-04 chapters/ch_intro.tex
General Backup

\chapter{Introduction}
\section{From Nuclear Forces to the Equation of State}
\section{Phases of Nuclear Matter}
\section{The Nuclear Equation of State}
\section{Previous Constraints}
\section{Motivation for building the S$\pi$RIT TPC}

>>>>

\chapter{Introduction}

\section{From Nuclear Forces to the Equation of State}
Isospin as a good quantum number at low energies 
Figure showing the nuclear forces for the pp, pn, nn 
Pauli exclusion 
inter particle distance , saturation density (maybe figure of all densities?)
Building the infinite matter
Statistical model 
Forces manifest in Energy/particle

\section{The Nuclear Equation of State}
Figure showing the binding energy vs p-n asym
Liquid drop model, mass equation, move to higher densities
Symmetric EoS asymmetric EoS(symmetry energy)
Density dependence of the symmetry energy

\section{Phases of Nuclear Matter}
gas liquid phase, gas, where are we
Progression through the heavy ion collision 
liquid, liquid gas, gas

\section{Studying EoS through Heavy Ion Collisions}
going from infinite matter to finite matter 
approximate nuclear matter with neutron rich radioactive ion beams
probe different asymmetries 
probe different densities with different beam energies 
Symmetry energy goes down at higher beam energies

\section{Boltzmann Ulong Uhlenbeck (BUU) Transport Code}
Does not reach equilibrium for all observable (hadrons) what about pions?
Build up a mean field picture (momentum dependent) unknown quantities here
Non equilibrium can be solved with Boltzman equation with collision term and solved by MC
Figure of transport simulation code showing collision progression 
Clustering is an issue 
Meson, resonance production

\section{Observables of interest to the EoS}
Particle yields of isospin opposites 
Flow??
Figure showing p-n observable lessens at high energy and from all densities

\section{Pion Production }
Figure showing delta resonance 
Figure showing pion's produced at 2po 
Figure showing fermi motion effect (not really sub threshold but ok)
(chemical potential model, delta isobar) prediction for pion ratio
pion mass is small momentum shifted by coulomb affecting shape of pion spectra

\section{Previous Constraints}
Figure showing GW constraint and other previous constraints 
FOPI data at 400 A MeV not as sensitive to symmetry energy 
Saturation density and lower constrained but issues at high density
conflicting analysis on FOPI data which was not intended to be used for Symm Energy
Can you group all the constraints to one nice plot???

\section{Motivation for building the S$\pi$RIT TPC}
Based on EOS TPC
High efficiency for detecting pions and other light charged particles 
Effort to reduce the experimental error bars on such spectra which theory could use
